### 2011-07-13 poster_gecco/poster.tex
Everything fits!

\renewcommand\refname{}
%\renewcommand\bibname{New Title2}

@@

\definecolor{lightorange}{rgb}{1.0, 0.9, 0.8}
\definecolor{lighteryellow}{cmyk}{0,0,0.1,0.0}
\definecolor{lightestyellow}{cmyk}{0,0,0.05,0.0}
\begin{poster}{
  columns = 3,
  % Show grid to help with alignment
  grid=no,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=white,
  bgColorTwo=white,
  borderColor=darkblue1,
  headerColorOne=blue1,
  headerColorTwo=darkblue1,
  headerFontColor=black,
  boxColorOne=white,
  boxColorTwo=white,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=no,
  headerborder=open,
  headerheight=0.09\textheight,
  headershape=roundedright,
  headershade=plain,
  headerfont=\normalsize\textsf, %Sans Serif
  boxshade=plain,
%  background=shade-tb,
  background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  {} % No eye catcher for this poster. If an eye catcher is present, the title is centered between eye-catcher and logo.
  % Title
  {\sf %Sans Serif
  %\bf% Serif
  \vspace{0em}{\huge Generating Gaits for Physical Quadruped Robots:} \\{\LARGE Evolved Neural Networks Vs. Local Parameterized Search}}
  % Authors
  {\sf %Sans Serif
  % Serif
  \vspace{.3em}\\{\normalsize Jason Yosinski, Jeff Clune, Diana Hidalgo, Sarah Nguyen, Juan Cristobal Zagal, Hod Lipson}\\\hspace{0.3em}
  \code{\footnotesize \{jy495, jeffclune, djh283, smn64\}@cornell.edu, jczagal@ing.uchile.cl, hod.lipson@cornell.edu}\hspace{3em}
  }
  % University logo
  {{\begin{minipage}{.25\textwidth}
    \hfill
    \includegraphics[height=5.0em]{cornellLogo}
  \end{minipage}}
  }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Abstract}{name=abstract,column=0,row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \input{abstract}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Platform}{name=platform,column=0,below=abstract}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The quadruped robot in this study was assembled from off-the-shelf components and parts
printed on the Objet Connex 500 3-D Printing System. It weighs 1.88 kg
with the on-board computer and measures approximately 38 centimeters
from leg to opposite leg in the crouch position depicted above.
The robot is actuated by 9 AX-12+
Dynamixel servos: one inner joint and one outer joint servo in each of
the four legs, and one servo at the center ``hip'' joint.  This final
unique servo allows the two halves of the robot to rotate with respect
to each other.

All of the computation for gait learning, fitness evaluation, and
robot control was performed on the compact, on-board CompuLab Fit-PC2,
running Ubuntu Linux 10.10.
All gait generation, learning, and fitness
evaluation code, except HyperNEAT, was written in Python and is
available on our website (http://bit.ly/geccogait).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Experimental Setup}{name=experimentalSetup,column=1}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pwfigg{wiiMote_crop.jpg}{robot_led_crop.jpg}{.6}{A Nintendo Wii
  remote tracked an IR LED on the robot, transmitting the (x,y)
  location via bluetooth.}

\pwfig[r]{linearInterp}{.6}{Motion was interpolated linearly between a
  stationary pose and the commanded gait $g(t)$.}

@@

The fitness was the Euclidian distance the robot
moved during a 12-second run on flat terrain.
The HyperNEAT gaits stressed the motors
more than the other gaits, so to encourage gaits that did not tax the
motors, we penalized gaits that caused the servos to stop
responding by a factor of 1/2.

The robot was always measured while in the \emph{ready} position
(shown in the first figure) to ensure fair fitness measurements. As
shown below the instantaneous robot limb configuration during the
first and last portions of the evaluation was an interpolation between
the initial ready position and $g(t)$; during the rest of the
evaluation, the robot followed the commanded gait exactly.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Parameterized Gaits}{name=parameterizedGaits,column=1,span=1,below=experimentalSetup}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Parameterized gaits were produced by the following gait function $g(t; \vec{\theta})$:

{
\footnotesize
\[
\vec{g}(t) =
\left[ {\begin{array}{c@{ }c@{ }c@{ }l@{ }l}
\amp \cdot \sin(2\pi t / \tau) & \             & \ \cdot \ m_F & \            & + C_I \\ % 0
\amp \cdot \sin(2\pi t / \tau) & \ \cdot \ m_O & \ \cdot \ m_F & \            & + C_O \\ % 1
\amp \cdot \sin(2\pi t / \tau) & \             & \             & \            & + C_I \\ % 2
\amp \cdot \sin(2\pi t / \tau) & \ \cdot \ m_O & \             & \            & + C_O \\ % 3
\amp \cdot \sin(2\pi t / \tau) & \             & \             & \ \cdot \ m_R  & + C_I \\ % 4
\amp \cdot \sin(2\pi t / \tau) & \ \cdot \ m_O & \             & \ \cdot \ m_R  & + C_O \\ % 5
\amp \cdot \sin(2\pi t / \tau) & \             & \ \cdot \ m_F & \ \cdot \ m_R  & + C_I \\ % 6
\amp \cdot \sin(2\pi t / \tau) & \ \cdot \ m_O & \ \cdot \ m_F & \ \cdot \ m_R  & + C_O \\ % 7
0                              & \             & \             & \            & + C_C \\ % 8
\end{array} } \right]
\]
}

\noindent with parameters in the following ranges:

{
\footnotesize
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Parameters        &                           &       \\
in $\vec{\theta}$ & Description               & Range \\
\hline
\hline
\amp         & Amplitude                 & [0, 400] \\
\hline
$\tau$       & Period                    & [.5, 8] \\
\hline
$m_O$        & Outer-motor multiplier    & [-2, 2] \\
\hline
$m_F$        & Front-motor multiplier    & [-1, 1] \\
\hline
$m_R$        & Right-motor multiplier    & [-1, 1] \\
\hline
\end{tabular}
\tablabel{parameters}
\label{tab:params}
\end{center}
}

Intuitively, SineModel5 starts with 8 identical sine waves of
amplitude $\amp$ and period $\tau$, multiplies the waves for all outer
motors by $m_O$, multiplies the waves for all front motors by $m_F$,
and multiplies the waves for all right motors by $m_R$.  To obtain the
actual motor position commands, these waves are offset by
fixed constants ($C_O = 40$ for outer
motors, $C_I = 800$ for inner motors, and $C_C = 512$ for the center hip motor) so that the base position (when the sine
waves are at 0) is approximately a crouch.
To keep the size of the model search space as
small as possible, we decided to keep the ninth (center) motor at a fixed neutral
position.

The \textbf{learning methods} used to search the parameterized gait
space were: \textbf{Random}, \textbf{Uniform random hill climbing},
\textbf{Gaussian random hill climbing}, \textbf{N-dimensional policy
  gradient ascent}, \textbf{Nelder-Mead simplex method}, \textbf{Linear
  regression}, and \textbf{SVM regression}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{HyperNEAT Gaits}{name=hyperneatGaits,column=1,span=1}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

HyperNEAT is an indirect encoding for evolving artificial neural
networks (ANNs) that is inspired by the way natural organisms
develop~\cite{stanley2009hypercube}. It evolves Compositional Pattern
Producing Networks (CPPNs)~\cite{stanley2007compositional}, each of
which is a genome that encodes an ANN
\pwfig{SpiderANN.jpg}{.6}{The ANN configuration used to generate gaits
  \cite{clune2011performance}.}\label{hyperneatLayout}
phenotype~\cite{stanley2009hypercube}. Each CPPN is itself a directed
graph, where the nodes in the graph are mathematical functions, such as sine or
Gaussian. The nature of these functions can facilitate the evolution
of properties such as symmetry (e.g.\ a Gaussian function) and repetition (e.g.\ a sine
function)~\cite{stanley2009hypercube, stanley2007compositional}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Results}{name=results,column=2,span=1,row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    By training on data collected in the lab, we were able to predict
    quadrotor drift quite accurately.  The below images show the
    actual versus predicted drift, including the directly predicted
    derivatives as well as the inferred (integrated) position.

    %\begin{multicols}{2}

      %\begin{center}
      %  \includegraphics[width=0.9\linewidth]{dec17_1_DataLog-1292574599_07_int}
      %\end{center}

    %\end{multicols}\vspace{-1em}

    %%%%%%%%%%%%%%%%%%%%%%
    \mbox{\hspace{0.3\linewidth}\rule{0.4\linewidth}{1pt}\hspace{0.3\linewidth}}\\

    Drift predictions under normal conditions, trained on data
    collected in similar conditions.
    \vspace{-.7em}

    \begin{multicols}{3}

      \begin{tabular}{ccc}
        \includegraphics[width=.9\linewidth]{robot_whitebg.jpg}
        &
        \includegraphics[width=.9\linewidth]{robot_whitebg.jpg}
        &
        \includegraphics[width=.9\linewidth]{robot_whitebg.jpg}
        \\

        \capt{Predicted versus actual x drift at each timestep in
          pixels per second.} & \capt{Predicted versus actual y drift
          at each timestep in pixels per second.} & \capt{Actual
          position versus position inferred from integrated
          predictions}
      \end{tabular}\\

    \end{multicols}\vspace{-1em}

    %%%%%%%%%%%%%%%%%%%%%%
    \mbox{\hspace{0.3\linewidth}\rule{0.4\linewidth}{1pt}\hspace{0.3\linewidth}}\\

    Predictions under artificially windy conditions, trained on data
    collected under normal conditions as well as windy conditions.
    \vspace{-.7em}

    \begin{multicols}{3}

      \begin{tabular}{ccc}
        \includegraphics[width=.9\linewidth]{robot_whitebg.jpg}
        &
        \includegraphics[width=.9\linewidth]{robot_whitebg.jpg}
        &
        \includegraphics[width=.9\linewidth]{robot_whitebg.jpg}
        \\

        \capt{Predicted vs. actual x drift} & \capt{Predicted
          vs. actual y drift} & \capt{Integrated position}
      \end{tabular}\\

      \end{multicols}\vspace{-1em}

    %%%%%%%%%%%%%%%%%%%%%%
    \mbox{\hspace{0.3\linewidth}\rule{0.4\linewidth}{1pt}\hspace{0.3\linewidth}}\\

    Although our algorithm was able to accurately predict drift, we
    are still working on getting the prediction code to be fast enough
    to control the quadrotor in live flight.  The SVM regression code
    runs quickly, but we're currently facing difficulties with delays
    due to I/O as well as a suboptimal configuration.\\

  }%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Conclusion}{name=conclusion,column=2,span=1,below=results}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    We are making strong progress towards predicting and removing
    quadrotor drift.  The drift is predicted fairly accurately via a
    60 dimensional sensor data vector from the quadrotor, and we hope
    to soon demonstrate a controller enhanced by the predicted drift. \vspace{.5em}
  }%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Abbreviated References}{name=references,column=0,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

    \footnotesize
    \bibliography{references.bib}
    \bibliographystyle{is-plain}
  }%
\end{poster}%
%
\end{document}

>>>>

\renewcommand\refname{}   % get rid of ``References'' title

@@

\definecolor{lightorange}{rgb}{1.0, 0.9, 0.8}
\definecolor{lighteryellow}{cmyk}{0,0,0.1,0.0}
\definecolor{lightestyellow}{cmyk}{0,0,0.05,0.0}
\begin{poster}{
  columns = 4,
  % Show grid to help with alignment
  grid=no,
  % Column spacing
  colspacing=1em,
  % Color style
  bgColorOne=white,
  bgColorTwo=white,
  borderColor=darkblue1,
  headerColorOne=blue1,
  headerColorTwo=darkblue1,
  headerFontColor=black,
  boxColorOne=white,
  boxColorTwo=white,
  % Format of textbox
  textborder=roundedleft,
  % Format of text header
  eyecatcher=no,
  headerborder=open,
  headerheight=0.075\textheight,
  headershape=roundedright,
  headershade=plain,
  headerfont=\normalsize\textsf, %Sans Serif
  boxshade=plain,
%  background=shade-tb,
  background=plain,
  linewidth=2pt
  }
  % Eye Catcher
  {} % No eye catcher for this poster. If an eye catcher is present, the title is centered between eye-catcher and logo.
  % Title
  {\sf %Sans Serif
  %\bf% Serif
  \vspace{.4em}{\huge Generating Gaits for Physical Quadruped Robots:} \\{\LARGE Evolved Neural Networks Vs. Local Parameterized Search}\vspace{.3em}}
  % Authors
  {\sf %Sans Serif
  % Serif
  \vspace{-.25em}{\normalsize Jason Yosinski, Jeff Clune, Diana Hidalgo, Sarah Nguyen, Juan Cristobal Zagal, Hod Lipson}\\\hspace{0.3em}
  \code{\footnotesize yosinski@cs.cornell.edu}\hspace{3em}
  }
  % University logo
  {{\begin{minipage}{.25\textwidth}
    \hfill
    \includegraphics[height=5.0em]{cornellLogo}
  \end{minipage}}
  }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Abstract}{name=abstract,column=0,row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    {\small
    \input{abstract}
    }
    \vspace{.5em}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Platform and Experimental Setup}{name=platform,column=0,below=abstract,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \small

@@

    The quadruped robot was assembled from off-the-shelf
    components and parts printed on the Objet Connex 500 3-D Printing
    System.
    % It weighs 1.88 kg with the on-board computer and measures 38
    % centimeters from leg to opposite leg in the crouch position
    % depicted above.
    The robot is actuated by 9 AX-12+ Dynamixel servos: 8 for the legs and one at the center ``hip'' joint.
    %This final unique servo allows
    %the two halves of the robot to rotate with respect to each other.

    All computation for gait learning, fitness evaluation, and
    robot control was performed on the compact, on-board CompuLab
    Fit-PC2, running Ubuntu Linux 10.10.  All gait generation,
    learning, and fitness evaluation code, except HyperNEAT, was
    written in Python and is available on our website
    (http://bit.ly/geccogait).

%  }
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  \headerbox{Experimental Setup}{name=experimentalSetup,column=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\pfigg{wiiMote_crop.jpg}{robot_led_crop.jpg}{1}{A Nintendo Wii
  remote tracked an IR LED on the robot, transmitting the (x,y)
  location via bluetooth.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Fitness Evaluation}{name=fitnessEvaluation,column=1}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The fitness was the Euclidian distance the robot moved during a
12-second run on flat terrain.  To encourage gaits that did not tax
the motors, we penalized gaits that caused the servos to stop
responding by a factor of 1/2.

\pfig{linearInterp}{1}{Motion was interpolated linearly between a
  stationary pose and the gait $g(t)$.}

The robot was always measured while in the \emph{ready} position
to ensure fair fitness measurements. As
shown above the instantaneous robot limb configuration during the
first and last portions of the evaluation was an interpolation between
the initial ready position and $g(t)$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Parameterized Gaits}{name=parameterizedGaits,column=1,span=1,below=fitnessEvaluation,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Parameterized gaits were produced by the following gait function $g(t; \vec{\theta})$:

\vspace{-.75em}

{
\tiny
\[
\vec{g}(t) =
\left[ {\begin{array}{c@{ }c@{ }c@{ }l@{ }l}
\amp \cdot \sin(2\pi t / \tau) & \             & \ \cdot \ m_F & \            & + C_I \\ % 0
\amp \cdot \sin(2\pi t / \tau) & \ \cdot \ m_O & \ \cdot \ m_F & \            & + C_O \\ % 1
\amp \cdot \sin(2\pi t / \tau) & \             & \             & \            & + C_I \\ % 2
\amp \cdot \sin(2\pi t / \tau) & \ \cdot \ m_O & \             & \            & + C_O \\ % 3
\amp \cdot \sin(2\pi t / \tau) & \             & \             & \ \cdot \ m_R  & + C_I \\ % 4
\amp \cdot \sin(2\pi t / \tau) & \ \cdot \ m_O & \             & \ \cdot \ m_R  & + C_O \\ % 5
\amp \cdot \sin(2\pi t / \tau) & \             & \ \cdot \ m_F & \ \cdot \ m_R  & + C_I \\ % 6
\amp \cdot \sin(2\pi t / \tau) & \ \cdot \ m_O & \ \cdot \ m_F & \ \cdot \ m_R  & + C_O \\ % 7
0                              & \             & \             & \            & + C_C \\ % 8
\end{array} } \right]
\]
}

\vspace{-.75em}

\noindent with parameters in the ranges:

\vspace{-.75em}

{
\scriptsize
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
Parameters        &                           &       \\
in $\vec{\theta}$ & Description               & Range \\
\hline
\hline
\amp         & Amplitude                 & [0, 400] \\
\hline
$\tau$       & Period                    & [.5, 8] \\
\hline
$m_O$        & Outer multiplier    & [-2, 2] \\
\hline
$m_F$        & Front multiplier    & [-1, 1] \\
\hline
$m_R$        & Right multiplier    & [-1, 1] \\
\hline
\end{tabular}
\tablabel{parameters}
\label{tab:params}
\end{center}
}

Intuitively, we start with 8 identical sine waves of
amplitude $\amp$ and period $\tau$, multiply the waves for all outer
motors by $m_O$, multiply the waves for all front motors by $m_F$,
and multiply the waves for all right motors by $m_R$.  To obtain the
actual motor position commands, these waves are offset by
fixed constants ($C_O = 40$ for outer
motors, $C_I = 800$ for inner motors, and $C_C = 512$ for the center hip motor) so that the base position (when the sine
waves are at 0) is approximately a crouch.
To keep the size of the model search space as
small as possible, we decided to keep the ninth (center) motor at a fixed neutral
position.

@@

The \textbf{learning methods} used to search the parameterized gait
space were: \textbf{Random}, \textbf{Uniform random hill climbing},
\textbf{Gaussian random hill climbing}, \textbf{N-dimensional policy
  gradient ascent}, \textbf{Nelder-Mead simplex method},
\textbf{Linear regression}, and \textbf{SVM regression}. A discussion
of each is in the paper.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{HyperNEAT Gaits}{name=hyperneatGaits,column=2,span=1}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \small

@@

    HyperNEAT is an indirect encoding for evolving artificial neural
    networks (ANNs) that is inspired by the way natural organisms
    develop~\cite{stanley2009hypercube}. It evolves Compositional
    Pattern Producing Networks
    (CPPNs)~\cite{stanley2007compositional}, each of which is a genome
    that encodes an ANN \pwfig{SpiderANN.jpg}{.7}{The ANN
      configuration used to generate gaits
      \cite{clune2011performance}.}\label{hyperneatLayout}
    phenotype~\cite{stanley2009hypercube}. Each CPPN is itself a
    directed graph, where the nodes in the graph are mathematical
    functions, such as sine or Gaussian. The nature of these functions
    can facilitate the evolution of properties such as symmetry
    (e.g.\ a Gaussian function) and repetition (e.g.\ a sine
    function)~\cite{stanley2009hypercube, stanley2007compositional}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Results}{name=results,column=3,span=1,row=0}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\small
\textbf{Parameterized Gaits}
\vspace{.5em}

\noindent A total of 1217 hardware fitness evaluations were performed to learn
parameterized gaits in three separate runs (200 random, 234 uniform, 284 Gaussian, 174
gradient, 172 simplex, 153 linear regression). The SVM-modeled method
was never successful.

%One reason the randomly-generated SineModel5 gaits were so effective
%may have been due to the SineModel5's bias toward regular, symmetric
%gaits.  This may have allowed the random strategy --- focusing on
%exploration --- to be competitive with the more directed strategies
%that exploit information from past evaluations.

\pfig{std_error}{1}{Average results ($\pm $ SE) for parameterized
  learning methods over three runs.  Linear regression found the
  fastest overall gait, followed by
  Nelder-Mead simplex.}

\textbf{HyperNEAT Gaits}
\vspace{.5em}

\noindent A total of 540 evaluations were performed for HyperNEAT, whose gaits
were the faster by far than the parameterized models.  The single best
gait found had a speed of 45.72 body lengths/minute, 66\% better than
the best non-HyperNEAT gait and 8.9 times faster than the hand-coded
gait.

Evaluation of HyperNEAT gaits was very noisy, which made learning
difficult. We tested one gait 11 times and found performance of 26
$\pm$ 13 body lengths/minute, with a max of 38 and a min of 3.

%Many effective HyperNEAT gaits were not preserved across generations
%because a single poor-performing trial could prevent their
%selection. The HyperNEAT learning curve would be smoother if the noise
%in the evaluations could be reduced or more than one evaluation per
%individual could be afforded.

\pfig{hnResults}{.8}{Average fitness ($\pm $ SE) of the highest
  performing individual at each generation.}

{\scriptsize
\begin{center}
\begin{tabular}{|r|c|c|c||c|}
\hline
                                         & Avg & SD \\
\hline                                    
\hline                                    
Previous hand-coded gait                 & 5.16   &   --     \\
\hline
Random search                            & 9.40   &   6.83   \\
\hline
Uniform Hill Climbing             & 7.83   &   4.56   \\
\hline
Gaussian Hill Climbing            & 10.03  &   6.00   \\
\hline
Policy Gradient Descent                  & 6.32   &   7.39   \\
\hline
Nelder-Mead simplex                      & 12.32  &   3.35   \\
\hline
Linear Regression                        & 14.01  &  12.88   \\
\hline
Evolved Neural Network              &        &          \\
(HyperNEAT)                              & 29.26  &   6.37   \\
\hline
\end{tabular}
\capt{Average and SD of the best gaits found
  during each of three runs, in body
  lengths/minute.}  \tablabel{results}
\end{center}
}

  }%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \headerbox{Abbreviated References}{name=references,column=2,below=hyperneatGaits,above=bottom}{
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

    \scriptsize
    \bibliography{references.bib}
    \bibliographystyle{is-plain}
  }%
\end{poster}%
%
\end{document}
